Extended Data

### 2022-03-04 doc/manuscript/Dow_manuscript_Nature.Rmd
update C sink statistics
#92

In recent decades, Earth's forests have sequestered ~20% of anthropogenic CO~2~ emissions, thereby slowing the pace of atmospheric CO~2~ accumulation and climate change[@friedlingstein_global_2021;@harris_global_2021].
A substantive portion of this CO~2~ sink occurs in temperate deciduous forests, which sequester >300 Tg C yr^-1^ [@pugh_role_2019]. <!-- See issue # 92: https://github.com/EcoClimLab/growth_phenology/issues/92. ALSO: The temperate deciduous sink is >300 Tg C yr-1, but Pugh et al. 2019 estimate that ~200 Tg C yr-1 is attributable to demography (forest regrowth), while >100 Tg C yr-1 is controlled by environmental drivers. The latter portion seems more likely to be sensitive to spring temperatures, and I originally cited this number, but upon further thought it's probably complex enough that that's a false distinction. --> 
The future behavior of this CO~2~ sink will play an important yet uncertain role in influencing atmospheric CO~2~ and climate change[@arora_carbon_2020;@friedlingstein_global_2020].

>>>>

In recent decades, tree growth in Earth's forests has more than offset losses from deforestation and other disturbances, such that a net forest CO~2~ sink of ~`r round(5.8*12/44,1)` Gt C yr^-1^ <!--net forest estimate in Harris et al. Table 2--> offsets ~`r round(5.8/32,1)*100`%<!--net forest estimate / fossil fuel & cement, (Harris et al. Table 2)--> of anthropogenic emissions[@harris_global_2021], dramatically slowing the pace of atmospheric CO~2~ accumulation and climate change.
Of this important C sink, ~`r round(3.6/7.6,2)*100`%<!-- temperate net / global net, (Harris et al. Table 1)--> occurs in temperate forests[@harris_global_2021], with temperate deciduous forests sequestering >0.3 Gt C yr^-1^ [@pugh_role_2019]. <!-- Pugh et al. 2019 estimate that the temperate deciduous sink is >300 Tg C yr-1, with ~200 Tg C yr-1  attributable to demography (forest regrowth) and >100 Tg C yr-1  controlled by environmental drivers.--> 
The future behavior of this C sink will play an important yet uncertain role in influencing atmospheric CO~2~ and climate change[@arora_carbon_2020;@friedlingstein_global_2020].
